### 2018-05-24 submission/manuscript.Rmd
merge tables together and update manuscript

---
title: ''
csl: peerj.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---

@@

***The Number of OTUs are Dependent on Polymerase:***
Differences in the range of the number of OTUs detected for fecal samples is dependent on the polymerase used [Figure 1]. Additionally, there is a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases [Figure 1]. There is an overall difference in the number of OTUs detected within fecal samples between polymerases at 35 cycles (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S1]. No differences between the polymerases was found based on a Tukey post-hoc test (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S2]. The polymerase dependent difference in the range of the number of OTUs also was observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across the number of cycles used [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between polymerases were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. The majority of differences for the number of OTUs detected in the Mock community is largely due to Kappa and Platinum differences to the other polymerases across the different number of cycles [Table S4]. Based on these observations in fecal and mock communities, it is clear that different polymerases result in a different total number of OTUs within a sample.

@@

***Sequence Error is Dependent on both Polymerase and Cycle Number:***
Differences in the median error rate varied by polymerase, with Kappa being the highest [Figure 4 & Table S5]. The differences in the median error rate between the polymerases also is dependent on the number of cycles, with Platinum and Kappa having the most differences versus other polymerases [Figure 4 and Table S6]. The total sequences with at least one error also is dependent on the number of cycles [Table S7 & S8]. These differences in sequences with at least one error is mostly due to differences in Accuprime^TM^ and Kappa versus the other polymerases [Table S7 & S8]. The differences in error rates were not due to polymerase dependent differences in base substitution rate [Figure S1]. These results suggest that sequence error is dependent on polymerase and the number of cycles, but is not attributable to a specific type. Based on these results, we examined whether chimeras also were dependent on polymerase and whether this also could affect the number of OTUs.

***Prevalence of Chimeric Sequences are Polymerase Dependent and Correlate with the Number of OTUs:***
There is significant differences in the chimera prevalence based on polymerase at all the number of cycles used (P-value `r ifelse(max(filter(kruskal_chimera_prev)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Differences in chimera prevalence between Platinum and all other polymerases accounted for the majority of these differences [Table S10]. Accuprime^TM^ had the lowest chimera prevalence of all polymerases regardless of whether chimera removal with VSEARCH was used [Figure 5A & 5B]. Additionally, there was a plateau in the total percent of chimeras that were removed that was similar for all polymerases [Figure 5C]. A positive correlation was observed between chimeric sequences and the number of OTUs for all polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion [Figure 6]. This data suggests that chimera prevalence depends on polymerase used and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

>>>>

---
title: ''
csl: peerj.csl
fontsize: 11pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---

@@

***The Number of OTUs are Dependent on Polymerase:***
Differences in the range of the number of OTUs detected for fecal samples is dependent on the polymerase used [Figure 1]. Additionally, there is a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases [Figure 1]. There is an overall difference in the number of OTUs detected within fecal samples between polymerases at 35 cycles (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S1]. No differences between the polymerases was found based on a Tukey post-hoc test (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S2]. The polymerase dependent difference in the range of the number of OTUs also was observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across the number of cycles used [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between polymerases were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S1]. The majority of differences for the number of OTUs detected in the Mock community is largely due to Kappa and Platinum differences to the other polymerases across the different number of cycles [Table S2]. Based on these observations in fecal and mock communities, it is clear that different polymerases result in a different total number of OTUs within a sample.

@@

***Sequence Error is Dependent on both Polymerase and Cycle Number:***
Differences in the median error rate varied by polymerase, with Kappa being the highest [Figure 4 & Table S3]. The differences in the median error rate between the polymerases also is dependent on the number of cycles, with Platinum and Kappa having the most differences versus other polymerases [Figure 4 and Table S4]. The total sequences with at least one error also is dependent on the number of cycles [Table S3 & S4]. These differences in sequences with at least one error is mostly due to differences in Accuprime^TM^ and Kappa versus the other polymerases [Table S3 & S4]. The differences in error rates were not due to polymerase dependent differences in base substitution rate [Figure S1]. These results suggest that sequence error is dependent on polymerase and the number of cycles, but is not attributable to a specific type. Based on these results, we examined whether chimeras also were dependent on polymerase and whether this also could affect the number of OTUs.

***Prevalence of Chimeric Sequences are Polymerase Dependent and Correlate with the Number of OTUs:***
There is significant differences in the chimera prevalence based on polymerase at all the number of cycles used (P-value `r ifelse(max(filter(kruskal_chimera_prev)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S3]. Differences in chimera prevalence between Platinum and all other polymerases accounted for the majority of these differences [Table S4]. Accuprime^TM^ had the lowest chimera prevalence of all polymerases regardless of whether chimera removal with VSEARCH was used [Figure 5A & 5B]. Additionally, there was a plateau in the total percent of chimeras that were removed that was similar for all polymerases [Figure 5C]. A positive correlation was observed between chimeric sequences and the number of OTUs for all polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion [Figure 6]. This data suggests that chimera prevalence depends on polymerase used and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

### 2018-05-24 submission/manuscript.tex
merge tables together and update manuscript

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\textbf{\emph{The Number of OTUs are Dependent on Polymerase:}}
Differences in the range of the number of OTUs detected for fecal
samples is dependent on the polymerase used {[}Figure 1{]}.
Additionally, there is a trend for lower number of cycles (15-20) to
result in a reduced range in the number of OTUs versus higher number of
cycles (25, 30, and 35) for all polymerases {[}Figure 1{]}. There is an
overall difference in the number of OTUs detected within fecal samples
between polymerases at 35 cycles (F-stat \textgreater{} 16.35, P-value =
9.7e-05) {[}Table S1{]}. No differences between the polymerases was
found based on a Tukey post-hoc test (P-value \textgreater{} 0.05)
{[}Table S2{]}. The polymerase dependent difference in the range of the
number of OTUs also was observed in the mock community samples {[}Figure
2{]}. Regardless if fecal or mock communities were used, the same
polymerases had high (Platinum) and low (Accuprime) number of OTUs and
this was consistent across the number of cycles used {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between polymerases were observed as early as 20 cycles in
the mock community (F-stat = 15.82, P-value = 0.002) {[}Table S3{]}. The
majority of differences for the number of OTUs detected in the Mock
community is largely due to Kappa and Platinum differences to the other
polymerases across the different number of cycles {[}Table S4{]}. Based
on these observations in fecal and mock communities, it is clear that
different polymerases result in a different total number of OTUs within
a sample.

@@

\textbf{\emph{Sequence Error is Dependent on both Polymerase and Cycle
Number:}} Differences in the median error rate varied by polymerase,
with Kappa being the highest {[}Figure 4 \& Table S5{]}. The differences
in the median error rate between the polymerases also is dependent on
the number of cycles, with Platinum and Kappa having the most
differences versus other polymerases {[}Figure 4 and Table S6{]}. The
total sequences with at least one error also is dependent on the number
of cycles {[}Table S7 \& S8{]}. These differences in sequences with at
least one error is mostly due to differences in
Accuprime\textsuperscript{TM} and Kappa versus the other polymerases
{[}Table S7 \& S8{]}. The differences in error rates were not due to
polymerase dependent differences in base substitution rate {[}Figure
S1{]}. These results suggest that sequence error is dependent on
polymerase and the number of cycles, but is not attributable to a
specific type. Based on these results, we examined whether chimeras also
were dependent on polymerase and whether this also could affect the
number of OTUs.

\textbf{\emph{Prevalence of Chimeric Sequences are Polymerase Dependent
and Correlate with the Number of OTUs:}} There is significant
differences in the chimera prevalence based on polymerase at all the
number of cycles used (P-value \textless{} 0.05) {[}Table S9{]}.
Differences in chimera prevalence between Platinum and all other
polymerases accounted for the majority of these differences {[}Table
S10{]}. Accuprime\textsuperscript{TM} had the lowest chimera prevalence
of all polymerases regardless of whether chimera removal with VSEARCH
was used {[}Figure 5A \& 5B{]}. Additionally, there was a plateau in the
total percent of chimeras that were removed that was similar for all
polymerases {[}Figure 5C{]}. A positive correlation was observed between
chimeric sequences and the number of OTUs for all polymerases {[}Figure
6{]}. This positive correlation was strongest for
Accuprime\textsuperscript{TM}, Platinum, and Phusion {[}Figure 6{]}.
This data suggests that chimera prevalence depends on polymerase used
and confirms that the number of OTUs is dependent on the prevalence of
these chimeric sequences.

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\textbf{\emph{The Number of OTUs are Dependent on Polymerase:}}
Differences in the range of the number of OTUs detected for fecal
samples is dependent on the polymerase used {[}Figure 1{]}.
Additionally, there is a trend for lower number of cycles (15-20) to
result in a reduced range in the number of OTUs versus higher number of
cycles (25, 30, and 35) for all polymerases {[}Figure 1{]}. There is an
overall difference in the number of OTUs detected within fecal samples
between polymerases at 35 cycles (F-stat \textgreater{} 16.35, P-value =
9.7e-05) {[}Table S1{]}. No differences between the polymerases was
found based on a Tukey post-hoc test (P-value \textgreater{} 0.05)
{[}Table S2{]}. The polymerase dependent difference in the range of the
number of OTUs also was observed in the mock community samples {[}Figure
2{]}. Regardless if fecal or mock communities were used, the same
polymerases had high (Platinum) and low (Accuprime) number of OTUs and
this was consistent across the number of cycles used {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between polymerases were observed as early as 20 cycles in
the mock community (F-stat = 15.82, P-value = 0.002) {[}Table S1{]}. The
majority of differences for the number of OTUs detected in the Mock
community is largely due to Kappa and Platinum differences to the other
polymerases across the different number of cycles {[}Table S2{]}. Based
on these observations in fecal and mock communities, it is clear that
different polymerases result in a different total number of OTUs within
a sample.

@@

\textbf{\emph{Sequence Error is Dependent on both Polymerase and Cycle
Number:}} Differences in the median error rate varied by polymerase,
with Kappa being the highest {[}Figure 4 \& Table S3{]}. The differences
in the median error rate between the polymerases also is dependent on
the number of cycles, with Platinum and Kappa having the most
differences versus other polymerases {[}Figure 4 and Table S4{]}. The
total sequences with at least one error also is dependent on the number
of cycles {[}Table S3 \& S4{]}. These differences in sequences with at
least one error is mostly due to differences in
Accuprime\textsuperscript{TM} and Kappa versus the other polymerases
{[}Table S3 \& S4{]}. The differences in error rates were not due to
polymerase dependent differences in base substitution rate {[}Figure
S1{]}. These results suggest that sequence error is dependent on
polymerase and the number of cycles, but is not attributable to a
specific type. Based on these results, we examined whether chimeras also
were dependent on polymerase and whether this also could affect the
number of OTUs.

\textbf{\emph{Prevalence of Chimeric Sequences are Polymerase Dependent
and Correlate with the Number of OTUs:}} There is significant
differences in the chimera prevalence based on polymerase at all the
number of cycles used (P-value \textless{} 0.05) {[}Table S3{]}.
Differences in chimera prevalence between Platinum and all other
polymerases accounted for the majority of these differences {[}Table
S4{]}. Accuprime\textsuperscript{TM} had the lowest chimera prevalence
of all polymerases regardless of whether chimera removal with VSEARCH
was used {[}Figure 5A \& 5B{]}. Additionally, there was a plateau in the
total percent of chimeras that were removed that was similar for all
polymerases {[}Figure 5C{]}. A positive correlation was observed between
chimeric sequences and the number of OTUs for all polymerases {[}Figure
6{]}. This positive correlation was strongest for
Accuprime\textsuperscript{TM}, Platinum, and Phusion {[}Figure 6{]}.
This data suggests that chimera prevalence depends on polymerase used
and confirms that the number of OTUs is dependent on the prevalence of
these chimeric sequences.

### 2018-05-24 submission/supplemental.Rmd
merge tables together and update manuscript

---
title: ''
csl: peerj.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: null
---

@@

**Table S1: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal Samples**

@@

fs_anova <- as.data.frame(read_csv("../data/process/tables/fecal_overall_anova_results.csv")) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level) %>% 
  mutate_at(vars(Sum.Sq:F.value), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2)))

colnames(fs_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycle")

@@

**Table S2: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal Samples**

@@

fs_tukey <- as.data.frame(read_csv("../data/process/tables/fecal_overall_tukey_results.csv")) %>% 
  mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level) %>% 
  rename(padj = `p adj`) %>% 
  mutate(padj = as.numeric(padj)) %>% 
  mutate_at(vars(padj), funs(format(., digits = 2, nsmall = 2)))

colnames(fs_tukey) <- c("Difference", "Lower", "Upper", "P Adjusted", "Comparison", "Cycle")

@@

**Table S3: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Mock Samples**

```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

mock_anova <- as.data.frame(read_csv("../data/process/tables/mock_overall_anova_results.csv")) %>% 
  mutate_at(vars(Sum.Sq:F.value), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level)

colnames(mock_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycle")

kable(mock_anova, format = "markdown", align = 'c', padding = 2)
```

**Table S4: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Mock Samples**

```{r supplemental_table4, echo=FALSE, message=FALSE, warning=FALSE}

mock_tukey <- as.data.frame(read_csv("../data/process/tables/mock_overall_tukey_results.csv")) %>% 
  mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level) %>% 
  rename(padj = `p adj`) %>% 
  mutate(padj = as.numeric(padj)) %>% 
  filter(padj < 0.05) %>% 
  arrange(padj) %>% 
  mutate_at(vars(padj), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  arrange(cycle)

colnames(mock_tukey) <- c("Difference", "Lower", "Upper", "P Adjusted", "Comparison", "Cycle")

kable(mock_tukey, format = "markdown", align = 'c', padding = 2)

**Table S5: Kruskal-Wallis Results of Differences in Per Base Error Rate between HiFi DNA Polymerases in Mock Samples**

@@

mock_error_rate_kruskal <- as.data.frame(read_csv("../data/process/tables/mock_error_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-sub_sample_level)

colnames(mock_error_rate_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle")

@@

**Table S6: Dunn's Post-Hoc Results of Differences in Per Base Error Rate between HiFi DNA Polymerases in Mock Samples**

@@

mock_error_rate_dunn <- as.data.frame(read_csv("../data/process/tables/mock_error_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh, -sub_sample_level) %>% 
  arrange(cycle)

colnames(mock_error_rate_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle")

@@

**Table S7: Kruskal-Wallis Results of Differences in Sequences with Error between HiFi DNA Polymerases in Mock Samples**

```{r supplemental_table7, echo=FALSE, message=FALSE, warning=FALSE}

mock_error_count_kruskal <- as.data.frame(
  read_csv("../data/process/tables/mock_error_count_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-sub_sample_level)

colnames(mock_error_count_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle")

kable(mock_error_count_kruskal, format = "markdown", align = 'c', padding = 2)

**Table S8: Dunn's Post-Hoc Results of Differences in Sequences with Error between HiFi DNA Polymerases in Mock Samples**

```{r supplemental_table8, echo=FALSE, message=FALSE, warning=FALSE}

mock_error_count_dunn <- as.data.frame(read_csv("../data/process/tables/mock_error_count_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh, -sub_sample_level) %>% 
  arrange(cycle)

colnames(mock_error_count_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle")

kable(mock_error_count_dunn, format = "markdown", align = 'c', padding = 2)

**Table S9: Kruskal-Wallis Results of Differences in Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

```{r supplemental_table9, echo=FALSE, message=FALSE, warning=FALSE}

mock_chimera_kruskal <- as.data.frame(
  read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-sub_sample_level)

colnames(mock_chimera_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle")

kable(mock_chimera_kruskal, format = "markdown", align = 'c', padding = 2)

**Table S10: Dunn's Post-Hoc Results of Differences in Chimera Prevalence between HiFi DNA Polymerase in Mock Samples**

```{r supplemental_table10, echo=FALSE, message=FALSE, warning=FALSE}

mock_chimera_dunn <- as.data.frame(read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh, -sub_sample_level) %>% 
  arrange(cycle)

colnames(mock_chimera_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle")

kable(mock_chimera_dunn, format = "markdown", align = 'c', padding = 2)

>>>>

---
title: ''
csl: peerj.csl
fontsize: 11pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: null
---

@@

**Table S1: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal and Mock Samples**

@@

fs_anova <- as.data.frame(read_csv("../data/process/tables/fecal_overall_anova_results.csv")) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level) %>% 
  mutate_at(vars(Sum.Sq:F.value), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  mutate(sample_type = "Fecal Sample") %>% 
  bind_rows(
    as.data.frame(read_csv("../data/process/tables/mock_overall_anova_results.csv")) %>% 
    mutate_at(vars(Sum.Sq:F.value), funs(round(., digits = 2))) %>% 
    mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    filter(sub_sample_level == 1000) %>% 
    select(-sub_sample_level) %>% 
    mutate(sample_type = "Mock Sample"))

colnames(fs_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycle", "Sample Type")

@@

**Table S2: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal and Mock Samples**

@@

fs_tukey <- as.data.frame(read_csv("../data/process/tables/fecal_overall_tukey_results.csv")) %>% 
  mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
  filter(sub_sample_level == 1000) %>% 
  select(-sub_sample_level) %>% 
  rename(padj = `p adj`) %>% 
  mutate(padj = as.numeric(padj)) %>% 
  mutate_at(vars(padj), funs(format(., digits = 2, nsmall = 2))) %>% 
  mutate(sample_type = "Fecal Sample") %>% 
  bind_rows(
    as.data.frame(read_csv("../data/process/tables/mock_overall_tukey_results.csv")) %>% 
    mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
    filter(sub_sample_level == 1000) %>% 
    select(-sub_sample_level) %>% 
    rename(padj = `p adj`) %>% 
    mutate(padj = as.numeric(padj)) %>% 
    filter(padj < 0.05) %>% 
    arrange(padj) %>% 
    mutate_at(vars(padj), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    arrange(cycle) %>% 
    mutate(sample_type = "Mock Sample"))

colnames(fs_tukey) <- c("Difference", "Lower", "Upper", "P Adjusted", "Comparison", "Cycle", "Sample Type")

@@

**Table S3: Kruskal-Wallis Results of Differences in Error Rate, Sequences with an Error, and Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

@@

mock_error_rate_kruskal <- as.data.frame(read_csv("../data/process/tables/mock_error_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-sub_sample_level) %>% 
  mutate(test_type = "Error Rate") %>% 
  bind_rows(
    as.data.frame(
    read_csv("../data/process/tables/mock_error_count_overall_kruskal_results.csv")) %>% 
    mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
    mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    select(-sub_sample_level) %>% 
    mutate(test_type = "Sequences with Error")) %>% 
  bind_rows(
    as.data.frame(
    read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")) %>% 
    mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
    mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    select(-sub_sample_level) %>% 
    mutate(test_type = "Chimera Prevalence"))

colnames(mock_error_rate_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle", "Test Type")

@@

**Table S4: Dunn's Post-Hoc Results of Differences in Error Rate, Sequences with an Error, and Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

@@

mock_error_rate_dunn <- as.data.frame(read_csv("../data/process/tables/mock_error_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh, -sub_sample_level) %>% 
  arrange(cycle) %>% 
  mutate(test_type = "Error Rate") %>% 
  bind_rows(
    as.data.frame(read_csv("../data/process/tables/mock_error_count_overall_dunn_results.csv")) %>% 
    mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
    filter(pvalue < 0.05) %>% 
    arrange(pvalue) %>% 
    mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    select(-bh, -sub_sample_level) %>% 
    arrange(cycle) %>% 
    mutate(test_type = "Sequences with Error")) %>% 
  bind_rows(
    as.data.frame(read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")) %>% 
    mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
    filter(pvalue < 0.05) %>% 
    arrange(pvalue) %>% 
    mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    select(-bh, -sub_sample_level) %>% 
    arrange(cycle) %>% 
    mutate(test_type = "Chimera Prevalence"))

colnames(mock_error_rate_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle", "Test Type")

@@
